Formalizing Stack Safety as a Security Property

### 2021-09-28 submission4/main.tex
Moved callee-saves

\paragraph{Limitations}

@@

Observable properties allow us to defer enforcement until a property
violation would become visible. Now we can identify when lazy policies
miss such violations, which are again susceptible to testing;
Table~\ref{tab:lazy-bug-table} summarizes the results of our evaluation.
The Lazy Tagging and Clearing
micro-policy from Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} tags each stack slot with the call depth
at which it was written, and enforces that it must be read from the
same depth. However, this allows violations of observable stack safety!
Our implementation of this policy, {\em PER\_DEPTH\_TAG}, has an error that we find
in testing. If, at depth \(d\), a callee \(A\) writes into its caller's
frame, then returns, and later another callee \(B\) at depth \(d\) reads the same
address and prints it, \(A\) has violated integrity in a way that later becomes visible,
and \(B\) has likewise violated confidentiality!

@@

%Per-activation tagging resolves the issue because tags that persist between
%calls will not become active again.
Our abstract properties have allowed us to identify an enforcement mechanism as
not really stack safe, and to validate a possible fix.
Unfortunately, Lazy Per-activation Tagging and Clearing
puts severe pressure on the tag cache, so it may not be usable in practice.
However, we conjecture that no lazy scheme can be fully stack safe
without using unique per-activation identifiers.

@@

Under some calling conventions, rather than the caller saving the non-argument
data from its registers
and clearing them (and therefore implicitly taking responsibility for
protecting this data),
the callee is responsible for this. But of course we may still wish for
those registers to be
protected, just as they would be in a caller-saves convention.

Intuitively, a caller expects a callee-saves register to be unchanged on
return: it
may change during the call, as long as it is restored. We similarly expect a callee-saves
register to be secret from the callee, except when it is copied to the stack! Both scenarios
reflect observational rather than stepwise stack safety.

\paragraph*{Discussion}

Observational properties are not only for lazy enforcement mechanisms---they reflect a useful
loosening of the stepwise properties. Consider a single register \(\reg\) that is saved.
It is copied to some stack address \(\addr\), violating stepwise confidentiality, and then
overwritten, violating stepwise integrity. Then before the return, it is restored to its
original value. In observational integrity terms, \(\reg\) is unchanged between call and return,
and in observational confidentiality terms, both the original and variant values are unchanged
from their originals, so that \(\reg\) is not in the \(\Delta\) set.  But \(\addr\) is in the
\(\Delta\) set, so confidentiality additionally requires that the value of \(\reg\) does not
leak through the callee-saves mechanism, for instance if the caller allocates but fails to
initialize more memory.

>>>>

\paragraph*{Limitations}

@@

Observable properties allow us to defer enforcement until a property
violation would become visible. Now we can identify when lazy policies
miss such violations, which are again susceptible to testing;
Table~\ref{tab:lazy-bug-table} summarizes the results of our evaluation.
The Lazy Tagging and Clearing
micro-policy from Roessler and DeHon \cite{DBLP:conf/sp/RoesslerD18} in fact
allows violations of observable stack safety!
Our implementation of this policy, {\em PER\_DEPTH\_TAG}, has an error that we find
in testing. If, at depth \(d\), a callee \(A\) writes into its caller's
frame, then returns, and later another callee \(B\) at depth \(d\) reads the same
address and prints it, \(A\) has violated integrity in a way that later becomes visible,
and \(B\) has likewise violated confidentiality!

@@

Our abstract properties have allowed us to identify an enforcement mechanism as
not really stack safe, and to validate a possible fix.
Unfortunately, Lazy Per-activation Tagging and Clearing
puts severe pressure on the tag cache, so it may not be usable in practice.
However, we conjecture that no lazy scheme can be fully stack safe
without using unique per-activation identifiers.

Another application of observational properties is characterizing a ``callee-saves''
calling convention.
Intuitively, a caller expects a callee-saves register to be unchanged on
return, but it
may change during the call, as long as it is restored. We similarly expect a callee-saves
register to be secret from the callee, except when it is copied to the stack. Both scenarios
reflect observational rather than stepwise stack safety.

@@
